Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-11 docs/google-research-awards-latam/main.tex
gitignore update

\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{color}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
%% macros
\newcommand{\ie}{i.e.}
\newcommand{\eg}{e.g.}
\newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
\newcommand{\Mar}[1]{\textbf{[[}{\color{blue} #1}\textbf{]]}}
\newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
\newcommand{\Comment}[1]{}

@@

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify} largely because of its
widespread use on the web. As common in software, the JS specification
changes regularly\footnote{Recently, the specification went through a
  bigger change compared to prior releases, called by the name of
  ECMAScript6 (ES6)~\cite{es6-features}} to accomodate pressing
demands~\cite{kangax} and these changes often entail sensible changes
in engine implementations that could lead to errors, including
regressions.  Test generation can help reduce the cost of testing, but
the lack of executable specifications is an important obstacle for
finding functional errors.

@@

The novelty of our proposal is the use of multiple engine
implementations (\eg{}, Google's V8, Microsoft's Chakra, etc.) to
assess input validity and to check output
correctness. \emph{Differential testing}\Fix{cite} has been applied in
a variety of contexts\Fix{cite cite}, but it has not been used to find
functional bugs in JS engines \MAB{That's wrong - it has been used at
  least two times: \cite{patra2016learning} and in jsfunfuzz (with a
  smaller scope - most likely regressions)}

@@

\begin{wrapfigure}[13]{r}[0pt]{0.45\textwidth}
\vspace{-5ex}
%\begin{figure}[htbp]
  \centering
  \includegraphics[trim=0 350 200 0,clip,width=0.5\textwidth]{google-awards-workflow}
  \label{fig:workflow}
  \caption{Workflow of Infrastructure.}
%\end{figure}
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs\Fix{cite} with the typical goal of finding
crashes. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are generated (\eg{},
mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
random-based\Fix{cite}) and whether or not coverage information is
taken into account in the fuzzing process. Figure~\ref{fig:workflow}
shows a generic pipeline of a fuzzer. JS files are provided as seeded
inputs to bootstrap the process. These files can originate from the
test suites of the engine codebases or from the bug reports in their
issue trackers. \Fix{elaborate}

\section{Related Work}

\Mar{rule of thumb: explain the
  contribution/novelty, then results achieved, and then how it relates
with our proposal.}
\Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
of C programs to generate invalid entries\Fix{the goal of a
   fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
  goal is to generate valid programs without undefined behavior to
  facilitate differential testing} and
find bugs in several C compilers\Fix{it is strange that you don't mention differential
  testing, which is central in CSmith, and the use of LLVM and GCC as
  oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
  follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
that exposes the LangFuzz to generate entries based in code fragments 
(language grammar, sample code, test suite) and the tool Mozilla 
Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
that implements a fuzzer based on JavaScript language to improve the 
testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
\Fix{...}

>>>>

\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{color}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
%% macros
\newcommand{\ie}{i.e.}
\newcommand{\eg}{e.g.}
\newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
\newcommand{\Mar}[1]{\textbf{[[Marcelo:~}{\color{blue} #1}\textbf{]]}}
\newcommand{\MAB}[1]{\textbf{[[Mateus:~}{\color{darkgreen} #1}\textbf{]]}}
\newcommand{\Comment}[1]{}

@@

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify} largely because of its
widespread use on the web. As common in software, the JS specification
changes regularly\footnote{Recently, the specification went through a
  bigger change compared to prior releases, called by the name of
  ECMAScript6 (ES6)~\cite{es6-features}} to accomodate pressing
demands of the community and these changes often entail sensible
changes in engine implementations~\cite{kangax} that could lead to
errors, including regressions.  Test generation can help reduce the
cost of testing, but the lack of executable specifications is an
important obstacle for finding functional errors.

@@

The novelty of our proposal is the use of multiple engine
implementations (\eg{}, Google's V8, Microsoft's Chakra, etc.) to
assess input validity and to check output correctness. Differential
testing\cite{McKeeman98differentialtesting} has been applied in a
variety of
contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17},
but it has not been thoroughly explored to find functional bugs in JS
engines. Patra and Pradel ran a small study, published in 2016 as
a tech report~\cite{patra2016learning}, where they found
discrepancies\Fix{confirm if they reported bugs}. The Mozilla
jsfunfuzz\Fix{elaborate a bit}.\Mar{Mateus, check if this sounds
  correct/fair to you and try to elaborate the jsfunfuzz part.}

\Fix{finalize}

@@

\begin{wrapfigure}[12]{r}[0pt]{0.45\textwidth}
\vspace{-5ex}
%\begin{figure}[htbp]
  \centering
  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
  \label{fig:workflow}
  \caption{Fuzzing Infrastructure.}
%\end{figure}
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs\Fix{cite} with the typical goal of finding
crashes. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are generated (\eg{},
mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
random-based\Fix{cite}) and whether or not coverage information is
taken into account in the fuzzing process. Figure~\ref{fig:workflow}
shows a generic pipeline of a fuzzer, instantiated to our problem. In
our case, JS files are provided as seeded inputs to bootstrap the
process. These files can originate from the test suites of the engine
codebases or from the bug reports in their issue trackers. The fuzzing
infrastrucutre selects randomly one of the inputs to fuzz with a given
tool, say the black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing
iteration produces a new file. For grammar-agnostic fuzzers, like
Radamsa, the infrastructure needs to detect and discard syntactically
invalid inputs. Semantically invalid inputs are detected dynamically
or with linters. Once the input is found to be valid, the
infrastructure invokes the oracle to check correctness. In case either
all engines consider the test output consistent (\ie{}, all pass or
all fail), the infrastructure discards the given input. Otherwise, it
considers that input as potentially fault-revaling and
interesting. Currently, we classify those alarms in two groups: HI and
LO. The HI group includes those warnings that manifest execution
errors spawned directly by the test (or its close neighborhood)
whereas the LO group includes the rest of the warnings. We found
empirically that \Fix{XX\%} of the warnings analyzed in the HI group
were confirmed (see Section~\ref{sec:results})

%% \section{Related Work}
%% \Mar{rule of thumb: explain the
%%   contribution/novelty, then results achieved, and then how it relates
%% with our proposal.}
%% \Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
%% of C programs to generate invalid entries\Fix{the goal of a
%%    fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
%%   goal is to generate valid programs without undefined behavior to
%%   facilitate differential testing} and
%% find bugs in several C compilers\Fix{it is strange that you don't mention differential
%%   testing, which is central in CSmith, and the use of LLVM and GCC as
%%   oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
%%   follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
%% that exposes the LangFuzz to generate entries based in code fragments 
%% (language grammar, sample code, test suite) and the tool Mozilla 
%% Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
%% that implements a fuzzer based on JavaScript language to improve the 
%% testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
%% \Fix{...}
